### 2014-03-14 HowtoHowtoCapon/submission/submit1/answer/answer.tex
la2pdf commit - 2014:03:14	01:57:07	(Fri14.Mar)
la2pdf commit - 2014:03:14	15:02:53	(Fri14.Mar)

\begin{enumerate}
\qi{What does somebody need to program in CUDA? Authors can mention that CUDA C is just C with a few extra language features to specify how to distribute the work across the cores. Authors can mention that there is a nvcc compiler, a profiler, a debugger, math libraries (CUFFT, CUBLAS), and a large number of examples of varying complexity, all from NVIDIA. Authors can mention that CUDA can be used on Windows, MacOSX, or Linux, with an NVIDIA graphics card. Authors can mention that there are also third party CUDA interfaces in Fortran and Python. When discussing the batch-optimized linear solver code from NVIDIA, the authors should cite the NVIDIA site, and also links to CULA and MAGMA, other CUDA versions of LAPACK or subsets thereof.}
\qi{Problems need to have high "arithmetic intensity" (the authors use "computational intensity") so that the cores stay busy. If there is not enough arithmetic, the cores sit idle waiting for data to be moved around. The authors do a nice job describing this situation on page 4 and the start of page 5.}
\ai{}
\qi{The authors use the term "arithmetic reduction". Unfortunately, reduction is an important word/topic in GPU work. Perhaps "minimizing arithmetic operations" would be better. Reduction is any N-to-1 mapping, which poses a conundrum for N cores having to combine their individual results at a single location all at the same time... you don't want the cores to all line up and wait their turn.}
\qi{On page 4, the authors talk about avoiding global memory, without get-ting into "coalesced" memory access patterns. This might merit a mention - for example, is at best only able to move one float for every 30 floats processed, and potentially much worse if care is not taken to use "coa-lesced memory access patterns (that avoid memory bank conflicts)". On page 5, the authors talk about "a collective access pattern that maximizes global memory bandwidth". Here too, the authors should perhaps use the "coalesced" term, since this is the term used in all of the GPGPU documentation.}
\end{enumerate}

@@

>>>>

\begin{enumerate}
\qi{What does somebody need to program in CUDA? Authors can mention that CUDA C is just C with a few extra language features to specify how to distribute the work across the cores. Authors can mention that there is a nvcc compiler, a profiler, a debugger, math libraries (CUFFT, CUBLAS), and a large number of examples of varying complexity, all from NVIDIA. Authors can mention that CUDA can be used on Windows, MacOSX, or Linux, with an NVIDIA graphics card. Authors can mention that there are also third party CUDA interfaces in Fortran and Python. When discussing the batch-optimized linear solver code from NVIDIA, the authors should cite the NVIDIA site, and also links to CULA and MAGMA, other CUDA versions of LAPACK or subsets thereof.}
\qi{Problems need to have high "arithmetic intensity" (the authors use "computational intensity") so that the cores stay busy. If there is not enough arithmetic, the cores sit idle waiting for data to be moved around. The authors do a nice job describing this situation on page 4 and the start of page 5.}
\ai{Thank you for those kind words. In the mentioned context we agree that "arithmetic" is likely a better alternative to "computational", and will make the relevant edits.}
%
\qi{The authors use the term "arithmetic reduction". Unfortunately, reduction is an important word/topic in GPU work. Perhaps "minimizing arithmetic operations" would be better. Reduction is any N-to-1 mapping, which poses a conundrum for N cores having to combine their individual results at a single location all at the same time... you don't want the cores to all line up and wait their turn.}
\ai{Yet again, very true! Your suggestion is much better, granted your permission we will use it.}
%
\qi{On page 4, the authors talk about avoiding global memory, without getting into "coalesced" memory access patterns. This might merit a mention - for example, is at best only able to move one float for every 30 floats processed, and potentially much worse if care is not taken to use "coalesced memory access patterns (that avoid memory bank conflicts)". On page 5, the authors talk about "a collective access pattern that maximizes global memory bandwidth". Here too, the authors should perhaps use the "coalesced" term, since this is the term used in all of the GPGPU documentation.}
\ai{You are right. Initially we sought to avoid as much GPU jargon as we could, but in its current form it probably just adds confusion to leave it out. Your suggestion sounded well.}
\end{enumerate}

@@

\newpage
\section{Changes to figures}
